---
title: "Luck-Corrected Peer Performance Analysis with PeerPerformance"
author: "David Ardia, Murilo Andre Peres Pereira, Benjamin Seguin"
output: rmarkdown::html_vignette
bibliography: null
vignette: >
  %\VignetteIndexEntry{Luck-Corrected Peer Performance Analysis with PeerPerformance}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r setup, include = FALSE}
knitr::opts_chunk$set(collapse = TRUE, comment = "#>", fig.width = 7,
                      fig.height = 3.4)
```

## Overview

`PeerPerformance` evaluates the performance of investment funds *relative to
their peers*, with a correction for luck that is robust to false discoveries.
For each fund $i$ it estimates three **peer performance ratios** that sum to
one:

- $\hat\pi^+_i$ -- the proportion of peers fund $i$ significantly **outperforms**,
- $\hat\pi^0_i$ -- the proportion of peers with **equal** performance,
- $\hat\pi^-_i$ -- the proportion of peers that **outperform** fund $i$.

The estimators implement the methodology of Ardia and Boudt (2018,
*Journal of Banking & Finance*); the modified Sharpe ratio test follows
Ardia and Boudt (2015, *Finance Research Letters*). A naive percentile rank
ignores that many funds may be statistically indistinguishable; the
false-discovery-rate (FDR) correction of Storey (2002) corrects for this.

```{r}
library(PeerPerformance)
data("hfdata")          # 60 monthly returns for 100 anonymized hedge funds
dim(hfdata)
```

## Alpha peer performance screening

`alphaScreening()` runs all pairwise tests and returns the three ratios for
each fund. With `factors = NULL` it compares raw returns; supply a `factors`
matrix to compare risk-adjusted alphas.

```{r}
set.seed(1234)
rets <- hfdata[, 1:15]
sc <- alphaScreening(rets, control = list(nCore = 1))
round(rbind(pipos = sc$pipos, pizero = sc$pizero, pineg = sc$pineg), 3)[, 1:6]
```

The three ratios sum to one for every fund. A `summary()` method ranks the
funds and reports the win/loss counts:

```{r}
summary(sc, top = 3)
```

The ratios are point estimates; `confint()` attaches confidence intervals by a
nonparametric peer (pairwise) bootstrap that resamples each fund's peers:

```{r}
set.seed(1234)
round(confint(sc, parm = "pipos")[1:6, ], 3)
```

The `plot()` method reproduces the Ardia and Boudt (2018) screening plot
(funds sorted by performance; stacked out-/equal-/under-performance bars with
the naive percentile-rank diagonal):

```{r screenfig}
plot(alphaScreening(hfdata[, 1:30], control = list(nCore = 1)))
```

## Sharpe and modified Sharpe ratios

```{r}
round(sharpe(rets[, 1:6]), 3)
round(msharpe(rets[, 1:6], level = 0.95), 3)
```

Equality of two funds' (modified) Sharpe ratios is tested with
`sharpeTesting()` / `msharpeTesting()`. The asymptotic test is the default; a
studentized bootstrap (recommended for short or autocorrelated series) is
requested with `control = list(type = 2)`.

```{r}
res <- msharpeTesting(hfdata[, 1], hfdata[, 2], level = 0.95)
c(dmsharpe = res$dmsharpe, tstat = res$tstat, pval = res$pval)
```

`sharpeScreening()` and `msharpeScreening()` build the peer performance ratios
from Sharpe (resp. modified Sharpe) comparisons instead of alphas.

## Comparing a fund (or group) against a separate peer group

The `Y` argument (or the convenience wrapper `targetPeerPerformance()`) screens
a chosen fund, or subset of funds, against a separate universe.

```{r}
focal <- hfdata[, 1]
peers <- hfdata[, 11:40]
res_xy <- alphaScreening(focal, Y = peers, control = list(nCore = 1))
round(c(pizero = res_xy$pizero, pipos = res_xy$pipos, pineg = res_xy$pineg), 3)
```

## Control parameters

All screening/testing functions share a `control` list. Common fields include
`nCore` (parallel cores), `lambda` (the $\lambda$ threshold for $\hat\pi^0$,
`NULL` = data-driven), `gammaPos`/`gammaNeg` (the one-sided thresholds, default
`0.4`/`0.6`), `hac` (HAC standard errors), and for the Sharpe/mSR routines
`type` (asymptotic/bootstrap), `nBoot`, and `bBoot`. See `?alphaScreening`.

## References

- Ardia, D., Boudt, K. (2018). The peer performance ratios of hedge funds.
  *Journal of Banking & Finance* **87**, 351--368.
- Ardia, D., Boudt, K. (2015). Testing equality of modified Sharpe ratios.
  *Finance Research Letters* **13**, 97--104.
- Storey, J. (2002). A direct approach to false discovery rates.
  *Journal of the Royal Statistical Society B* **64**(3), 479--498.
